Study of the numerical solution of X-Modes equations around the hybrid resonnance

### 2015-01-26 report/intro.tex
working on refs, add reflectometers exp, Dumont paper

\section{Introduction}
Modelling various phenomena in plasmas is of practical importance for developing new sources of energy 
based on plasma fusion, see the ITER project\footnote{www.iter.org}. 
In particular, this article concentrates on studying a phenomenon of a hybrid resonance \cite{Stix}, 
which is observed in experiments  \textcolor{red}{insert refs}\cite{} and 
mathematically is described as non-regularity of
the solutions of Maxwell equations in plasmas under strong background magnetic field \cite{Despres_2014}. 
The energy deposit is resonant and may exceed by far the energy 
exchange which occurs in Landau damping \textcolor{red}{ref}. 
Contrary to the Landau damping, however, 
hybrid resonance appears in a simpler model coupling 
fluid equations with the non electrostatic part of Maxwell equations.

>>>>

\section{Introduction}
Modelling various phenomena in plasmas is of practical importance for developing new sources of energy 
based on plasma fusion, see the ITER project\footnote{www.iter.org}. 
In particular, this article concentrates on studying a phenomenon of hybrid resonance \cite{Stix}, 
which is observed in experiments \cite{reflectometers_2006, reflectometers_2010, Dumont_2005} and 
mathematically is described as the non-regularity of
the solutions of Maxwell equations in plasmas under strong background magnetic field \cite{Despres_2014}. 
The energy deposit is resonant and may exceed by far the energy 
exchange which occurs in Landau damping \cite{}. 
Contrary to the Landau damping, however, 
hybrid resonance appears in a simpler model coupling 
fluid equations with the non electrostatic part of Maxwell equations.

### 2015-01-26 report/proc.tex
add some files
working on refs, add reflectometers exp, Dumont paper

%
%\dedicated{\it Dedicated to Maurice Dupont} %if necessary
%
\begin{abstract} ... \end{abstract}
%
\begin{resume} ... \end{resume}
%
%
\maketitle
\textcolor{red}{should we add Olivier Lafitte and Remi Sart anywhere in the proceeding ?}\\
%!!!!!!!!!!!todo !!!!!!!!!!!

@@

\begin{thebibliography}{99}
\bibitem{stable_yee_plasma_current} F. da Silva M. Campos Pinto, B. Despres and S. Heuraux, Stable Coupling of the Yee Scheme with a Linear Current Model,
2014
\bibitem{Despres_2014} Després, B., Imbert-Gérard, L. M. and Weder, R. (2014). Hybrid resonance of Maxwell's equations in slab geometry. Journal de Mathématiques Pures et Appliquées, 101(5), 623-659.
\bibitem{LMIG_thesis} Imbert-Gérard, L. M. (2013). Analyse mathématique et numérique de problèmes d'ondes apparaissant dans les plasmas magnétiques (Doctoral dissertation, Université Pierre et Marie Curie-Paris VI).
\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
\bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
Handbook of mathematical functions
\end{thebibliography}

>>>>

%
%\dedicated{\it Dedicated to Maurice Dupont} %if necessary
%
\begin{abstract}
\input{abstract}
\end{abstract}
%
\begin{resume} 
\input{resume}
\end{resume}
%
%
\maketitle
\textcolor{red}{should we add Olivier Lafitte and Remi Sart anywhere in the proceeding ?}\\
%!!!!!!!!!!!todo !!!!!!!!!!!

@@

\begin{thebibliography}{99}
\bibitem{stable_yee_plasma_current} Da Silva F., Campos Pinto M., Despres B. and Heuraux S., (2014) Stable Coupling of the Yee Scheme with a Linear Current Model,
\bibitem{reflectometers_2006} Da Silva, F., Heuraux, S and  Manso, M. (2006). Developments on reflectometry simulations for fusion plasmas: application to ITER position reflectometers. Journal of plasma physics, 72(06), 1205-1208.
\bibitem{reflectometers_2010}Da Silva, F., Heuraux, S., Gusakov, E. Z., and Popov, A. (2010). A Numerical Study of Forward-and Backscattering Signatures on Doppler-Reflectometry Signals. Plasma Science, IEEE Transactions on, 38(9), 2144-2149.
\bibitem{Despres_2014} Després, B., Imbert-Gérard, L. M. and Weder, R. (2014). Hybrid resonance of Maxwell's equations in slab geometry. Journal de Mathématiques Pures et Appliquées, 101(5), 623-659.
\bibitem{Dumont_2005} Dumont, R. J., Phillips, C. K., and Smithe, D. N. (2005). Effects of non-Maxwellian species on ion cyclotron waves propagation and absorption in magnetically confined plasmas. Physics of Plasmas (1994-present), 12(4), 042508.
\bibitem{LMIG_thesis} Imbert-Gérard, L. M. (2013). Analyse mathématique et numérique de problèmes d'ondes apparaissant dans les plasmas magnétiques (Doctoral dissertation, Université Pierre et Marie Curie-Paris VI).
\bibitem{brenner} Brenner, S. C. and Scott, R. (2008). The mathematical theory of finite element methods (Vol. 15). Springer.
\bibitem{Stix} Stix, T. H. (1992). Waves in plasmas. Springer.
\bibitem{Morawetz} Morawetz, C. S. (1962). The limiting amplitude principle. Communications on Pure and Applied Mathematics, 15(3), 349-361.
\bibitem{abramowitz_stegun} Abramowitz M. and Stegun I. A., eds. (1972). Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. New York: Dover Publications.
Handbook of mathematical functions
\end{thebibliography}
